My title

### 2024-03-10 paper/paper.qmd
update simulated data
update change

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

For the actual data we can use the 2020 Cooperative Election Study (CES) (@main_data)
```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and highest education
#| echo: false
#| warning: false
#| message: false

ces2020 <- read_csv(here("data/analysis_data/analysis_data.csv"))

ces2020 |>
  ggplot(aes(x = education, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Highest education",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

Define $y_i$ is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\mbox{gender}_i$ is the gender of the respondent and $\mbox{education}_i$ is the education of the respondent.  
We could estimate the parameters using `stan_glm()`. Note that the model is a generally accepted short-hand.  In practice rstanarm converts categorical variables into a series of indicator variables and there are multiple coefficients estimated. In the interest of run-time we will randomly sample 1,000 observations and fit the model on that, rather than the full dataset.

#linear regression example
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

#logistic regression example
\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{gender}_i +\beta_2 \times \mbox{education}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5)\\
\beta_1 &\sim \mbox{Normal}(0, 2.5)\\
\beta_2 &\sim \mbox{Normal}(0. 2.5)
\end{align}

@@

first_model <-
  readRDS(file = here::here("model/first_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

Weaknesses and next steps should also be included.

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

>>>>

# Introduction
Cooperative Election Study (CES) (@main_data) aims to study American electoral dynamics during 2022 elections period

# Data {#sec-data}
For the actual data we can use the 2022 Cooperative Election Study (CES) (@main_data)

## Source and Methodology

## Variables
```{r}
#| label: fig-variables
#| fig-cap: Brief summary of variables types
#| echo: false
#| warning: false
#| message: false

ces2022 <-  read_csv(file = here::here("data/raw_datas/raw_datas.csv"))
    col_types =
      cols(
        "votereg" = col_integer(),
        "presvote20post" = col_integer(),
        "gender" = col_integer(),
        "race" = col_integer()
      )
ces2022
```
  After downloading @dataverse, We using @get_dataframe_by_name to access the CES. We select and save the data that we are most care about, which are "votereg", "presvote20post", "race", and "gender4". "votereg" represent the voter registration status. To be more specific, whether they are registered to vote or not. "presvote20post" records the president that voter select in the election of 2020. “race" describe the voter's raical or ethnic group, and "gender4" refer to the gender of voters.
  However, when we access the raw data, there are some variables that we are not interested in. Therefore, we use the codebook to delve into the details. We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020. We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump. We use @tidyverse to filter to the voters that we care about and label them with meaningful title. In addition，CES also provide the information for the gender of the voter. However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman. Therefore, we filter the gender by using @tidyverse. When the variable "gender" is 1, this indicates "man", but we rename all "man" to "male". When the variable "gender" is 2, it refers to "woman". We also rename all "woman" to "female". Finally, the codebook also define different "race" from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other. We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
  To better understand the raw data, a summary table had been drawn in order to provide more details for each variables, explaining the variables we select.

## Measurements
```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and race
#| echo: false
#| warning: false
#| message: false

ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))

ces2022 |>
  ggplot(aes(x = race, fill = voted_for)) +
  stat_count(position = "dodge") +
  geom_text(stat='count', aes(label=..count..), position=position_dodge(width=0.9), vjust=-0.25, color="black") +
  facet_wrap(facets = vars(gender4)) +
  theme_minimal() +
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

@@

And also planes (@fig-vote). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

Define $y_i$ is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\mbox{gender}_i$ is the gender of the respondent and $\mbox{race}_i$ is the race of the respondent.  
We could estimate the parameters using `stan_glm()`. Note that the model is a generally accepted short-hand.  In practice rstanarm converts categorical variables into a series of indicator variables and there are multiple coefficients estimated. In the interest of run-time we will randomly sample 500 observations and fit the model on that, rather than the full dataset.

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{gender}_i +\beta_2 \times \mbox{education}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5)\\
\beta_1 &\sim \mbox{Normal}(0, 2.5)\\
\beta_2 &\sim \mbox{Normal}(0. 2.5)
\end{align}

@@

us_political_preferences <-
  readRDS(file = here::here("model/first_model.rds"))
```

@@

modelsummary(
  list(
    "Support Biden" = us_political_preferences
  ),
  statistic = "mad"
)

```

@@
